Modeling thermal dust emission with two components: application to the {\it PLANCK} HFI maps

### 2014-08-09 ms.tex
tweak single-pixel spectrum example figure caption

\begin{figure}
\begin{center}
\epsfig{file=sed.eps, width=3.3in}
\caption{\label{fig:sed} Observed SED (black points and error bars) and 
best-fit thermal dust emission models for a single $N_{side}$=2048 pixel in the
Polaris flare region. The best-fit two-component model (black line) is derived 
based on \PLANCK~217-857 GHz and SFD 100$\mu$m at full $6.1'$ resolution. Note 
that the two lowest-frequency data points were not used in the two-component 
fit shown, while the three lowest-frequency data points were not used in the 
\cite{planckdust} single-MBB fit shown (cyan).}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\epsfig{file=sed.eps, width=3.3in}
\caption{\label{fig:sed} Observed SED (black points and error bars) and 
best-fit thermal dust emission models for a single $N_{side}$=2048 pixel in the
Polaris flare region. The best-fit two-component model (black line) is derived 
via the MCMC procedure of $\S$\ref{sec:mcmc}, based on \PLANCK~217-857 GHz and 
SFD 100$\mu$m at full $6.1'$ resolution. Note that the two lowest-frequency 
data points were not used in the two-component fit shown, while the three 
lowest-frequency data points were not used in the \cite{planckdust} single-MBB 
fit shown (cyan).}
\end{center}
\end{figure}
